ISYE 6501

### 2022-09-12 hw2/submission.Rmd

### Part 1: Cross Validation for finding best knnn model

@@

### Exploratory Data Analysis

@@

\* From the above graph, we can see that increasing the value of 'K' beyond 4 yields very low marginal benefit. \* Both 3 and 4 appear to be good values of 'K' and can be used depending on the use case. In this example, since we know that there are 3 classes, we expect 3 to be a more appropriate choice.

@@

From the confusion matrix, we can infer the following: \* Cluster 3 shows highest proportion of setosa class. In fact it encompasses 100% of that class. \* Cluster 2 has the highest proportion of versicolor class. \* Cluster 1 has the highest proportion of virginia class.

@@

### Accuracy in individual classes

>>>>

### Part 1: Cross Validation for finding best knn model

@@

### Exploratory Data Analysis (for getting the best predictor combinations)

@@

\* From the above graph, we can see that increasing the value of 'K' beyond 4 yields very low marginal benefit. \* Both 3 and 4 appear to be good values of 'K' and can be used depending on the use case. In this example, since we know that there are 3 classes, we expect 3 to be a more appropriate choice. (\*Best value of k for our analysis\*)

@@

From the confusion matrix, we can infer the following: \* Cluster 3 shows highest proportion of setosa class. In fact it encompasses 100% of that class. \* Cluster 2 has the highest proportion of versicolor class. \* Cluster 1 has the highest proportion of virginica class.

@@

### Accuracy in individual classes (to see how well clustering predicts flower type)
